---
title: "Pre-processing task"
author: 'Student number: 8520000'
output: 
  pdf_document:
  df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r include=FALSE}
data <- read_csv('./Data/normal.csv')

store <- read_csv('./Data/DA1920_store.csv')
  
test <- read_csv('./Data/DA1920_train.csv')

# merging 

join <- store %>% 
  left_join(test) %>% 
  select(-X11, -X12)
```


## Introduction
In this report I will be looking at sales data from a large drug story chain. I will begin by looking at the data provided and do some initial pre processing. I will then conduct some exploratory analysis of the data. Based on the results, I will conduct further pre-processing. Finally I will fit a very basic model and interpret the results. 

## Pre-processing

We are provided with three data sets, one with information on various stores, and a training and testing data set with information on sales, customers. The first preprocessing step is to join these data sets, on the store variable.




## Exploratory analysis
We can look at the effect of a few variables on sales, for example we might want to find out if certain days of the week tend to have more sales than others: 

```{r, echo=FALSE}
join %>%
  group_by(DayOfWeek) %>% 
  mutate(DayOfWeek =recode(DayOfWeek, 
                         `1` = 'Monday', 
                         `2` = 'Tuesday',
                         `3` = 'Wednesday',
                         `4` = 'Thursday',
                         `5` = 'Friday',
                         `6` = 'Saturday',
                         `7` = 'Sunday')) %>%
  summarise(Sales = mean(Sales)) %>%
  ggplot()+
  aes(x = reorder(DayOfWeek, -Sales),
      y = Sales,
      fill = DayOfWeek)+
  geom_col()+
  theme_minimal()+ 
  labs(x = "Day of the Week",
       fill = "Day of the Week")
  
```



## Further pre-processing

## 

## Conclusion